Papers

### 2025-10-14 papers.qmd
update

@@

-   Brand, C. O., Brady, D., & Stafford, T. (in press). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). *Cognitive Science*. [Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).

@@

>>>>

-   Jones, A., Petrovskaya, E., & Stafford, T. (2024). [Exploring the multiverse of analysis options for the alcohol Stroop](https://link.springer.com/article/10.3758/s13428-024-02377-5). Behavior Research Methods, 56(4), 3578-3588. [[preprint](https://psyarxiv.com/prfu2/)],[code/data](https://osf.io/utnx2/files/osfstorage)]

@@

-   Brand, C. O., Brady, D., & Stafford, T. (in press). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://doi.org/10.1111/cogs.70126). *Cognitive Science*. [Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).

@@

- Arjmandi-Lari, Z., Mantzarlis, A., Stafford, T. (2025). [Threats to the sustainability of Community Notes on X](https://arxiv.org/abs/2510.00650). arXiv preprint arXiv:2510.00650
